---
title: "Assignment 1"
output:
  pdf_document: default
  html_notebook: default
---

QUESTION 1 

Calculate continuous daily excess returns of SP500 (“^GSPC”) for the period from 1/1/2014 until 12/31/2014 using overnight Fed Funds rates as risk-free rates.
```{r}
data <- read.csv(file='SP500_NB2014.csv')
#head(data)
Excess.return <- ((data$SP500Returns - data$RIFSPFF_N.B) / 360 / 100)
head(Excess.return)
```
QUESTION 2    

Calculate daily log returns of both exchange rates
```{r}
library(quantmod)
library(xts)
library(zoo)

getFX("USD/JPY", src="oanda")
getFX("GBP/USD", src="oanda")
head(USDJPY, 15)
head(GBPUSD, 15)

USDJPY.rtn <- diff(log(USDJPY$USD.JPY)) # Compute log returns USDJPY
head(USDJPY.rtn)

GBPUSD.rtn <- diff(log(GBPUSD$GBP.USD)) # Compute log returns GBPUSD
head(GBPUSD.rtn)

```

Calculate sample min, mean, sd, skewness, kurtosis, max of log returns for both exchange rates
```{r}
library (fBasics)
library(timeDate)
library(timeSeries)
dataPath <- "~/UChicago/Q2/Financial_Analytics/"
data1 <- read.table(paste(dataPath,'USDJPY.csv',sep = '/'), header=TRUE)
data2 <- read.table(paste(dataPath,'GBPUSD.csv',sep = '/'), header=TRUE)
#head(data1)
#head(data2)

dat1 <- data1$X..USD.JPY. <- as.numeric(gsub(",","",data1$X..USD.JPY.))
#head(data1)
dat2 <- data2$X..GBP.USD. <- as.numeric(gsub(",","",data2$X..GBP.USD.))
#head(data2)

basicStats(dat1)
basicStats(dat2)
```

Test hypothesis H0:μ=0 against alternative H0:μ≠0
```{r} 
t.test(dat1)
t.test(dat2)
```
Since pvalue < 5% for both USDJPY (dat1) and GBPUSD (dat2) we reject the null hypothesis that there's no difference between the means and conclude that a significant difference does exist